\hspace{-1mm}{J-ReCoVer}:~Java~Reducer~Commutativity~Verifier\thanks{The work was supported by the Czech Science Foundation project 17-12465S.}\vspace*{-2mm}

### 2019-07-29 draft.tex
4
one bloody referrence
Added authors and Czech acknowledgement

\title{\hspace{-0.1cm}{J-ReCoVer}:~Java~Reducer~Commutativity~Verifier}
\author{}
\institute{}
\hide{
\author{
Yu-Fang Chen\inst{1}\inst{2}
\and
Chang-Yi Chiang\inst{2}
\and
Hsin-Hung Lin\inst{1}
\and
Wei-Tsung Kao\inst{1}
\and
Yean-Fu Wen\inst{2}
\and
Wei-Cheng Wu\inst{1}
}
\institute
{
Institute of Information Science, Academia Sinica, Taiwan
\and
Graduate Institute of Information Management, National Taipei University, Taiwan
}}
\author{}
\institute{}

@@

\vspace*{-4mm}\begin{abstract}

The MapReduce framework for data-parallel computation was first proposed by
Google~\cite{dean04} and later implemented in the Apache Hadoop
project. Under the MapReduce framework, a reducer computes output
values from a sequence of input values transmitted over the network. Due to
non-determinism in data transmission, the order in which input values arrive at
the reducer is not fixed. In relation to this, the \emph{commutativity problem}
of reducers asks if the output of a reducer is independent of the order of its
inputs. Indeed, there are several advantages for a reducer to be commutative,
e.g., the verification problem of a MapReduce program can be reduced to the
problem of verifying a sequential program. We present the tool J-ReCoVer (Java
Reducer Commutativity Verifier) that implements effective heuristics for reducer
commutativity analysis. J-ReCoVer is the first tool that is specialized in
checking reducer commutativity. Our experimental results over 118 benchmark
examples collected from open repositories are very positive; J-ReCoVer correctly
handles over 97~\% of them.

\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace*{-4mm}
\section{Introduction} \label{section:introduction}
\vspace*{-1mm}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

@@

%Various forms of sequentialisation are behind further research works too, 
Various forms of sequentialisation are also used in works dealing with the concept 
of \emph{robustness} of event-driven
asynchronous programs~\cite{ahmed2017:robustness} or works dealing with programs
running under some \emph{relaxed memory
models}~\cite{ahmed2013:robustness,AbdullaACLR13,AbdullaACLR12}. However, their
computation models are again quite different from that of reducers, and
their results cannot be directly applied.
Besides verification, another interesting research direction is the
\emph{synthesis} of MapReduce programs~\cite{SmithA16}, which uses commutativity analysis
as a component of its framework.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Notations and Definitions} \label{section:integer-reducers}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{-3mm}
\section{Evaluation} \label{section:exp}
\vspace{-2mm}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

J-ReCoVer failed in three cases out of the considered ones because the three
reducers use more complicated control structures than what J-ReCoVer currently
supports. Namely, they use a branch statement before entering the loop, i.e.,
they have the form of
$\ite{g}{(s_1;\rloop\{s_2\};s_3)}{(s'_1;\rloop\{s'_2\};s'_3)}$. In theory, such
a program can be handled by more sophisticated program transformation. For
example, we can merge the two loops and push the outer branch condition into the
merged loop. Extensions of J-ReCoVer to be able to handle such constructions,
together with a support for more data types, belong among our future works.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{-2mm}
\bibliographystyle{splncs-sorted}
\bibliography{refs}

>>>>

\title{\hspace{-1mm}{J-ReCoVer}:~Java~Reducer~Commutativity~Verifier\thanks{The
work was supported by the Czech Science Foundation project
17-12465S.}\vspace*{-2mm}}

\author{
Yu-Fang Chen\inst{1,2}
\and
Chang-Yi Chiang\inst{2}
\and
Luk\'{a}\v{s} Hol\'{\i}k\inst{3}
\and
Wei-Tsung Kao\inst{1}
\and
Hsin-Hung Lin\inst{1}
\and
Tom\'{a}\v{s} Vojnar\inst{3}
\and
Yean-Fu Wen\inst{2}
\and
Wei-Cheng Wu\inst{1}
}
\institute
{
Institute of Information Science, Academia Sinica, Taiwan
\and
Graduate Institute of Information Management, National Taipei University,
Taiwan
\and
FIT,  IT4I Centre of Excellence,Brno University of Technology, Czechia
}

@@

\vspace*{-4mm}\begin{abstract} The MapReduce framework for data-parallel
computation was first proposed by Google~\cite{dean04} and later implemented in
the Apache Hadoop project. Under the MapReduce framework, a reducer computes
output values from a sequence of input values transmitted over the network. Due
to non-determinism in data transmission, the order in which input values arrive
at the reducer is not fixed. In relation to this, the \emph{commutativity
problem} of reducers asks if the output of a reducer is independent of the order
of its inputs. Indeed, there are several advantages for a reducer to be
commutative, e.g., the verification problem of a MapReduce program can be
reduced to the problem of verifying a sequential program. We present the tool
J-ReCoVer (Java Reducer Commutativity Verifier) that implements effective
heuristics for reducer commutativity analysis. J-ReCoVer is the first tool that
is specialized in checking reducer commutativity. Our experimental results over
118 benchmark examples collected from open repositories are very positive;
J-ReCoVer correctly handles over 97~\% of them. \end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace*{-5mm}\section{Introduction}\label{section:introduction}\vspace*{-2mm}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%!!!!!!!!!!!!!!!!!!!!!!!!
\enlargethispage{5mm}
%!!!!!!!!!!!!!!!!!!!!!!!!

@@

%Various forms of sequentialisation are behind further research works too, 
Various forms of sequentialisation are also used in works dealing with the
concept of \emph{robustness} of event-driven asynchronous
programs~\cite{ahmed2017:robustness} or works dealing with programs running
under some \emph{relaxed memory
models}~\cite{ahmed2013:robustness,AbdullaACLR13,AbdullaACLR12}. However, their
computation models are again quite different from that of reducers, and their
results cannot be directly applied. Besides verification, another interesting
research direction, using commutativity analysis as a component, is
\emph{synthesis} of MapReduce programs~\cite{SmithA16}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace*{-2mm} \section{Notations and Definitions}
\label{section:integer-reducers} \vspace*{-1mm}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\vspace{-3mm}
\section{Evaluation} \label{section:exp}
%\vspace{-2mm}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
\enlargethispage*{4mm}
%!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!

@@

J-ReCoVer failed in three cases out of the considered ones because the three
reducers use more complicated control structures than what J-ReCoVer currently
supports. Namely, they use a branch statement before entering the loop, i.e.,
they have the form of
$\ite{g}{(s_1;\rloop\{s_2\};s_3)}{(s'_1;\rloop\{s'_2\};s'_3)}$. In theory, such
a program can be handled by more sophisticated program transformation. For
example, we can merge the two loops and push the outer branch condition into the
merged loop. Extensions of J-ReCoVer to be able to handle such constructions,
together with a support for more data types, is among our future directions.

@@

%!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
\enlargethispage*{4mm}
%!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{-2mm}
\bibliographystyle{splncs-sorted}
\bibliography{refs}
